---
title: "About the Roller Package"
author: "Ethan P. Marzban"
date: "`r Sys.Date()`"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{Vignette Title}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r setup, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
library(roller)
```

### General Information

This package is designed to simulate rolling a specificed `device()` a specified number of times. 

\ 

### Device:

Users are able to specify any type of device, so long as the number of sides is greater than one and the probabilities obey the basic axioms of probability (i.e. are nonnegative, between 0 and 1, and sum to 1). The default is a fair "coin" with two sides ("1" and "2") of equal probability:

```{r}
fair_coin <- device()
fair_coin
```

You can also specify nonstandard devices, of any length:

```{r}
tri_die <- device(c("1", "2", "3"), prob = c(1/3, 1/3, 1/3))
tri_die
```

\ 

### Rolls:

Users are also able to simulate rolling a device using the `roll()` function. The function takes an object of class "device" and rolls it a specified number of times (`times` must be a positive integer).

```{r}
roll(fair_coin, 2)
roll(tri_die, 100)
```

\ 

### Plotting:

This package comes with a default `plot()` function, which produces a frequency barchart of the rolls of a device. 

```{r}
die <- device(sides = 1:6, prob = rep(1/6, 6))
rolls100 <- roll(die, 100)
plot(rolls100)
```

\ 

### Some Examples:

Here are some examples of how to use the advanced functionality of the `Roller` Package:

```{r}
# roll fair 8-sided die
set.seed(123)
fair_dev <- device(sides = letters[1:8], prob = rep(1/8, 8))
fair500 <- roll(fair_dev, times = 500)

# summary method
summary(fair500)

# extracting roll in position 500
fair500[500]

# replacing last roll
fair500[500] <- 'a'
fair500[500]

# adding 100 rolls
fair600 <- fair500 + 100
summary(fair600)

# plot method
plot(fair500)
```
